Exploring probability distributions for bivariate temporal granularities

### 2019-11-18 main.Rmd
levels of granularities iumpact on visualisation

Creating a visualisation requires a number of nuanced judgements. However, we exploit some features of layers and faceting to come up with a recommendation system while visualizing the distribution of the "dependent" variable across bivariate temporal granularities. The general framework of visualizing the distribution invloves a faceting approach with one temporal granularity plotted along the x-axis, the other one across facet and the dependent time series variable on the y-axis. Different distribution plots might be appropriate depending on which features of the distrbution we are interested to look at, the levels of time granularities being plotted, how granularities interact and number of observations available. We will look at each of these aspects separately and analyze the effect of each on visualization. While we accomplish that, we need to bear in mind that any customised species of visualization might be constructed by varying the set of mappings between data properties and visual attributes such as position, shape and color.

@@

Choice of plots depend on the levels(very high/high/medium/low) of the two granularities plotted. The criteria for different levels could be based on usual cognitive power while comparing across facets and display size available to us.Space and resolution become a problem if the number of levels of facet variables is too high. Hence, plot choices will also vary depending on which granularity is placed on the x-axis and which one across facets.

@@

Space and cognitive power both are constrained if the number of levels of facet variables is very high. So as a general rule, we should avoid plotting a temporal granularity with very high levels across facets.

 - If levels of both the granularities are low, then any distribution plots might be chosen depending on which feature of the distribution who is interested to look at.

@@

 - If level of the granularity plotted across x-axis is low, then any distribution plots might be chosen depending on which feature of the distribution who is interested to look at, irrespective of the number of the levels of the facet variable.

@@

>>>>

Creating a visualisation requires a number of nuanced judgements. However, we exploit some features of layers and faceting to come up with a recommendation system while visualizing the distribution of the "dependent" variable across bivariate temporal granularities. The general framework of visualizing the distribution invloves a faceting approach with one temporal granularity plotted along the x-axis, the other one across facet and the dependent time series variable on the y-axis. Different distribution plots might be appropriate depending on which features of the distrbution we are interested to look at, the levels of time granularities being plotted, how granularities interact and number of observations available. We will look at each of these aspects separately and analyze the effect of each on visualization.

While we accomplish that, we need to bear in mind that any customised species of visualization might be constructed by varying the set of mappings between data properties and visual attributes such as position, shape and color. We are trying to address problems where even with good aesthetic qualities and good data, the graph might be confusing or misleading because of how people process the information.

@@

The levels (very high/high/medium/low) of the two granularities plotted might have an impact on the choice of plots. The criteria for different levels could be based on usual cognitive power while comparing across facets and display size available to us. Space and resolution become a problem if the number of levels of facet variables is too high. Hence, plot choices will also vary depending on which granularity is placed on the x-axis and which one across facets.

@@

 <!-- - If levels of both the granularities are low, then any statistical distribution plot might be chosen depending on which feature of the distribution one is interested to look at.  -->

  - If level of the granularity plotted across x-axis is low or medium, then any distribution plots might be chosen depending on which feature of the distribution needs focus, irrespective of the number of the levels of the facet variable.

@@

@@

  - - If levels of granularities plotted are medium, empirical based methods of statistical distribution are preferred as they use less space by design than most density based methods.
